\begin{rubric}{Employment History}
% \\textbf{Community Witch,} Village of Frying Pans.
%
% Blank lines result in extra space!
%
% \entry*[2013 -- 2015]%
% 	\textbf{Lecturer.} Information Technology Department, School of Engineering, Science and Technology, XYZ College.
%
\entry*[Jun 2018 -- Present]%
    \textbf{Technical Engineer, Luxtron, United Arab Emirates}\par
    Led the transition towards lighting and control systems.\par
    Designed and optimized lighting control schematics and commissioning processes. Collaborated with cross-functional teams to deliver customized control solutions.
    
\entry*[May 2024 -- Aug 2024]%
    \textbf{Graduate Researcher, Georgia Institute of Technology}\par
    Graduate researcher, a part of the \href{https://sites.gatech.edu/human-augmented-analytics-group/}{Human-Augmented Analytics Group}\par
    Implemented a full ML pipeline and researched whether LSTM models could be democratized on different building data.\par
    Published findings and models on \href{https://huggingface.co/spaces/GaTech-NREL/LSTM-forecaster}{HuggingFace Spaces} and \href{https://github.com/nkapila6/lstm-bgd2}{Github}.

\entry*[Aug 2019 -- Sept 2019]%
    \textbf{R\&D Trainee, Helvar, Finland}\par
    Evaluated intelligent wireless nodes for lighting control systems.\par
    Created technical documentation for AC-DC converters in LED lighting.\par
    Presented market research findings for Middle Eastern lighting trends.

\entry*[2017 -- 2018]%
    \textbf{Research Intern, Indian Institute of Technology, Delhi}\par
    Developed simulations for quadrotor systems using MATLAB Simulink.\par
    Analyzed mechanical systems leading to quadrotor design optimizations.
\end{rubric}